Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-11 paper.qmd
Added initial link plots

@@

error_df_one_curvy_abs <- error_df_one_curvy_abs |>
  mutate(error_cat_n = if_else(tSNE1 <= 0.25 & tSNE2 <= 0.25, "selected", "deselected")) |> ## high_error points
  mutate(error_cat_n2 = if_else(tSNE2 >= 1.2, "selected", "deselected")) ## corner points

@@

plot_tsne_dens <- error_df_one_curvy_abs_deselected12 |>
  ggplot(aes(x = tSNE1,
             y = tSNE2)) +
  geom_point(alpha=0.7, color = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected12,
             aes(x = tSNE1, y = tSNE2),
             alpha=0.7, color = "#800026", size = 3) +
  theme(aspect.ratio = 1) +
  interior_annotation("a2",
                      position = c(0.08, 0.9),
                      cex = 2)

plot_tsne_dens_selected <- error_df_one_curvy_abs_deselected11 |>
  ggplot(aes(x = tSNE1,
             y = tSNE2)) +
  geom_point(alpha=0.7, color = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected11,
             aes(x = tSNE1, y = tSNE2),
             alpha=0.7, color = "#800026", size = 3) +
  theme(aspect.ratio = 1) +
  interior_annotation("b2",
                      position = c(0.08, 0.9),
                      cex = 2)
```

@@

```{r}
#| label: langevitour-c-shaped-tsne-proj
#| eval: false

data_c_shaped_n <- data_c_shaped |>
  select(-type) |>
  mutate(type = factor(error_df_one_curvy_abs$error_cat_n2,
                          levels=c("deselected", "selected")))

df_model_data_n <- bind_rows(df_bin_dens_clust, data_c_shaped_n)

langevitour::langevitour(df_model_data_n[1:(length(df_model_data_n)-1)],
                         lineFrom = tr_from_to_df_dens_clust$from,
                         lineTo = tr_from_to_df_dens_clust$to,
                         group = factor(df_model_data_n$type,
                                        c("deselected", "selected", "model")),
                         levelColors = c('#d9d9d9', '#800026', "#000000"),
                         pointSize = c(1.5, 3, 0))
```

@@

@@

>>>>

df_bin_dens_clust_temp <- df_bin_dens_clust

error_df_one_curvy_abs_temp <- error_df_one_curvy_abs

@@

error_df_one_curvy_abs <- error_df_one_curvy_abs |>
  mutate(error_cat_n = if_else(emb1 <= 0.25 & emb2 <= 0.25, "selected", "deselected")) |> ## high_error points
  mutate(error_cat_n2 = if_else(emb2 >= 1.2, "selected", "deselected")) ## corner points

@@

plot_tsne_dens <- error_df_one_curvy_abs_deselected12 |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.7, color = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected12,
             aes(x = emb1, y = emb2),
             alpha=0.7, color = "#800026", size = 3) +
  theme(aspect.ratio = 1) +
  interior_annotation("a2",
                      position = c(0.08, 0.9),
                      cex = 2)

plot_tsne_dens_selected <- error_df_one_curvy_abs_deselected11 |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.7, color = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected11,
             aes(x = emb1, y = emb2),
             alpha=0.7, color = "#800026", size = 3) +
  theme(aspect.ratio = 1) +
  interior_annotation("b2",
                      position = c(0.08, 0.9),
                      cex = 2)
```

@@

```{r}
#| label: link-plts-c-shaped-data
#| eval: false

df_exe_c_shaped_data <- comb_all_data_model_error(
  highd_data = one_c_shaped_data,
  nldr_data = tsne_one_c_shaped,
  model_highd = df_bin_dens_clust_temp,
  model_2d = df_bin_centroids_dens_clust,
  error_data = error_df_one_curvy_abs_temp)

show_error_link_plots(point_data = df_exe_c_shaped_data,
                      edge_data = tr_from_to_df_dens_clust)
```

@@

tsne_minst_scaled_temp <- tsne_minst_scaled |>
  rename(c("emb1" = "tSNE1",
           "emb2" = "tSNE2"))

@@

```{r}
#| label: link-plts-mnist
#| eval: false

df_exe_mnist <- comb_all_data_model(
  highd_data = training_data_mnist,
  nldr_data = tsne_minst_scaled_temp,
  model_highd = df_bin_mnist,
  model_2d = df_bin_centroids_dens_clust)

show_link_plots(point_data = df_exe_mnist,
                edge_data = tr_from_to_df_dens_clust)
```
